---
title: "EPPS 6323: Lab02 R Programming Basics II"
author: "Chakrayuddh Kimsovanna"
format: html
editor: visual
---

# R Programming Basic Commands

(Adapted from ISLR Chapter 3 Lab: Introduction to R)

## Indexing Data using \[\]

```{r}
A=matrix(1:16,4,4)
A
A[2,3]
A[c(1,3),c(2,4)]
A[1:3,2:4]
A[1:2,]
A[,1:2]
A[1,]
A[-c(1,3),] # -c() removes rows 1 and 3
A[-c(1,3),-c(1,3,4)]
dim(A) # Dimensions
```

## Loading Data from GitHub (remote)

```{r}

# Running each function to test which reads data faster
time1 = proc.time()
Auto=read.csv("https://raw.githubusercontent.com/datageneration/knowledgemining/master/data/Auto.csv",header=T,na.strings="?")
proc.time()-time1

time2 = proc.time()
Auto=read.table("https://raw.githubusercontent.com/datageneration/knowledgemining/master/data/Auto.data")
proc.time()-time2

time3 = proc.time()
Auto=read.csv("https://raw.githubusercontent.com/datageneration/knowledgemining/master/data/Auto.csv")
proc.time()-time3

# It turns out the result varies a lot after multiple test. However, the third function reads the data quickest for the most time, followed by the second function, and then the first one.

# Check on data
dim(Auto)
Auto[1:4,] # select rows
Auto=na.omit(Auto)
dim(Auto) # The difference is that the null values are removed from that row
names(Auto)
```

## Load data from ISLR website

```{r Loaddata_from_web}
Auto=read.table("https://www.statlearning.com/s/Auto.data",header=T,na.strings="?")
dim(Auto)
```

## Additional Graphical and Numerical Summaries

```{r}
# plot(cylinders, mpg)
plot(Auto$cylinders, Auto$mpg)
attach(Auto)
plot(cylinders, mpg)
cylinders=as.factor(cylinders)
plot(cylinders, mpg)
plot(cylinders, mpg, col="red")
plot(cylinders, mpg, col="red", varwidth=T)
plot(cylinders, mpg, col="red", varwidth=T,horizontal=T)
plot(cylinders, mpg, col="red", varwidth=T, xlab="cylinders", ylab="MPG")
hist(mpg)
hist(mpg,col=2)
hist(mpg,col=2,breaks=15)
#pairs(Auto)
pairs(~ mpg + displacement + horsepower + weight + acceleration, Auto)
plot(horsepower,mpg)
# identify(horsepower,mpg,name) # Interactive: point and click the dot to identify cases
summary(Auto)
summary(mpg)
```

## Linear Regression

```{r}
ptbu=c("MASS","ISLR")
install.packages("MASS", "ISLR", repos='http://cran.us.r-project.org')
lapply(ptbu, require, character.only = TRUE)
library(MASS)
library(ISLR)

# Simple Linear Regression

fix(Boston)
names(Boston)
attach(Boston)
lm.fit=lm(medv~lstat,data=Boston)
lm.fit
summary(lm.fit)
names(lm.fit)
coef(lm.fit)
confint(lm.fit)
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="confidence")
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="prediction")
# The difference between "confidence" and "prediction" is that the first shows the range where we expect the mean value to be, while the latter shows the range where we expect a single new value to be.

plot(lstat,medv)
abline(lm.fit)
abline(lm.fit,lwd=3)
abline(lm.fit,lwd=3,col="red")
plot(lstat,medv,col="red")
plot(lstat,medv,pch=16)
plot(lstat,medv,pch="+")
plot(1:20,1:20,pch=1:20)
par(mfrow=c(2,2))
plot(lm.fit) 
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```

## Multiple Linear Regression

```{r}
lm.fit=lm(medv~lstat+age,data=Boston)
summary(lm.fit)
lm.fit=lm(medv~.,data=Boston)
summary(lm.fit)
library(car)
vif(lm.fit)
lm.fit1=lm(medv~.-age,data=Boston)
summary(lm.fit1)
lm.fit1=update(lm.fit, ~.-age)
```

## Non-linear Transformations of the Predictors

```{r}
lm.fit2=lm(medv~lstat+I(lstat^2))
summary(lm.fit2)
lm.fit=lm(medv~lstat)
anova(lm.fit,lm.fit2)
par(mfrow=c(2,2))
plot(lm.fit2)
lm.fit5=lm(medv~poly(lstat,5))
summary(lm.fit5)
summary(lm(medv~log(rm),data=Boston))
```

## Qualitative Predictors

```{r}
# fix(Carseats)
names(Carseats)
lm.fit=lm(Sales~.+Income:Advertising+Price:Age,data=Carseats)
summary(lm.fit)
attach(Carseats)
contrasts(ShelveLoc)
```

## Interaction Terms (including interaction and single effects)

```{r}
summary(lm(medv~lstat*age,data=Boston))
```
